% Copyright (C) 2015 by Ivan Valbusa 
% <ivan dot valbusa at univr dot it>
% -------------------------------------------------------
% 
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.

\documentclass[10pt]{beamer}

\usetheme{Verona}

\title{Verona -- a theme for Beamer}
\subtitle{Version 0.1a}
\author[Ivan Valbusa]{Ivan Valbusa\texorpdfstring{\\}{}\scriptsize\texttt{ivan dot valbusa at univr dot it}}
\institute[University of Verona]{Department of Philology, Literature, and Linguistics\\
University of Verona}
\date{November 27, 2015}

\begin{document}

% ----------- FRAME ------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]
\titlepage
\end{frame}
% ----------- FRAME ------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[b,plain]

\begin{alertblock}{Warning}
This is package is a beta version.\\
Some or all the elements could change in the next versions.
\end{alertblock}

\vfill

\color{gray}
\small
\noindent Copyright \copyright\ 2015 Ivan Valbusa.
 \bigskip

\noindent This package is author-maintained. 
Permission is granted to copy, distribute and/or modify this software under the 
terms of the LaTeX Project Public License, version 1.3c ora later (\url{http://latex-project.org/lppl}). This software is provided ''as is'', without warranty of any kind, either expressed or implied, including, but not limited to, the implied warranties of merchantability and fitness for a particular purpose.

 \bigskip
 
\noindent If you have any questions, feedback or requests please email me at \texttt{ivan dot valbusa at univr dot it}. If you need specific features not already implemented, remember to attach the example files.

\bigskip

\end{frame}
% ----------- FRAME ------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{How to use the theme?}

If you can use Beamer than you can use this theme:
\begin{description}
\item[\TeX Live] \$ \alert{\texttt{texdoc beamer}}
\item[Online] \url{http://bitbucket.org/rivanvx/beamer}
\end{description}

\bigskip

Templates:\\
\alert{\texttt{usr/local/texlive/\the\year/texmf-dist/doc/latex/beamer/solutions} }

\smallskip

This folder is in the \TeX Live distribution\\
installed on your computer!
\end{frame}
% ----------- FRAME ------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{How to load the theme?}

\begin{block}{If you do not like sectioning}
\verb!\usetheme{Verona}!
\end{block}

\begin{block}{If you like sectioning}
\verb!\usetheme[showheader]{Verona}!
\end{block}

\begin{alertblock}{Color options}
\verb!\usetheme[blue]{Verona}!\\
\verb!\usetheme[red]{Verona}!\\
\verb!\usetheme[gray]{Verona}!\\
\end{alertblock}
\begin{alertblock}{Boxes}
\verb!\usetheme[colorblocks]{Verona}!\\
\end{alertblock}
\begin{alertblock}{Frame title}
\verb!\usetheme[graytitle]{Verona}!
\end{alertblock}

\end{frame}
% ----------- FRAME ------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setbeamertemplate{background canvas}[vertical shading][top=gray,bottom=gray,middle=white,midpoint=0.9]
\begin{frame}[plain]{}
\vspace*{7cm}
\small
\textcolor{black!10}{Typeset with \LaTeX{} and Beamer class}
\end{frame}
\end{document}
